Supporting information: Copulas reveal complex and informative dependencies propagating throughout ecology

### 2019-05-15 SupportingInformation.Rmd
small chnages suggested by Shya, Lawrence, Van

\textbf{Phenological and population data on aphids.}
Data pre-processing for the aphid data was the same as 
that of @Sheppard2016,
but we excluded one of the 11 sites they used in order to only use sites with at least 30 
years data.

>>>>

\textbf{Phenological and population data on aphids.}
Data pre-processing for the aphid data was the same as that of @Sheppard2016, 
except that years for which data was unavailable were excluded rather than being 
replaced by median values. We also excluded one of the 11 sites they used in 
order to only use sites with at least 30 years data.
